Stylistic Context Clustering for Token-Level Author Diarization

### 2017-12-31 paper/paper.tex
no message
Weird fixes.

\abstract{ 
In this paper we present an approach to tackle the PAN 2016 author diarization and intrinsic plagiarism detection problem. We propose a method for unsupervised text diarization based on clustering of tokens using contextual style features obtained with a sliding window. There are two variants of our approach - one that uses different features based on the document being analyzed, and one that uses a fixed feature space and tries to adopt if for clustering with a trainable feature transformation. We have evaluated our approach on the available datasets from PAN 2016.
}

@@

For both Models A and B we calculated standard errors and wanted to obtain $95\%$ t-based confidence intervals. Since the test sets are small, D’Agostino and Pearson’s normality test with p-value $0.05$ was performed first. The Model A data in all tasks did not provide enough evidence to reject the null hypothesis that a sample comes from a normal distribution. In test of Model B's both $F_1$-scores, the data provided enough evidence to reject the null hypothesis.

>>>>

\abstract{ 
In this paper we present an approach to tackle the PAN 2016 author diarization and intrinsic plagiarism detection problem. We propose a method for unsupervised text diarization based on clustering of tokens using contextual style features obtained with a sliding window. There are two variants of our approach - one that uses different features based on the document being analyzed, and one that uses a fixed feature space and tries to adopt it for clustering with a trainable feature transformation. We have evaluated our approach on the available datasets from PAN 2016.
}

@@

For both Models A and B we calculated standard errors and wanted to obtain $95\%$ t-based confidence intervals. Since the test sets are small, D’Agostino and Pearson’s normality test with signficance level $0.05$ was performed first. The Model A data in all tasks did not provide enough evidence to reject the null hypothesis that a sample comes from a normal distribution. In test of Model B's both $F_1$-scores, the data provided enough evidence to reject the null hypothesis.
